% !TEX encoding = UTF-8 Unicode
%!TEX root = thesis.tex
% !TEX spellcheck = en-US
%%=========================================

\addcontentsline{toc}{section}{Acknowledgenment}
\begin{center}
\textbf{\textit{{\color{blue}\underline{ACKNOWLEDGEMENT}}}}
\end{center}

	First and foremost, I would like to express my hearty thanks and indebtedness to my supervisor \textbf{\textit{\color{blue} Mr. M. K. Singh}}, Department of Electronics Engineering, Indian Institute of Technology (Banaras Hindu University), Varanasi for his enormous help and encouragement throughout the course of this thesis. His technical knowledge and insight have given me an excellent background in the field of my work. His excellent guidance, perseverance, invaluable suggestions made this work possible and complete.\\
\indent My profound gratitude to \textbf{\textit{\color{blue} Prof. S. Jit, Head, Department of Electronics Engineering, Indian Institute of Technology (BHU), Varanasi}} for providing necessary facilities in order to perform necessary simulation study.\\
\indent		I would also like to thanks all the faculty members and the librarians for their kind cooperation and encouragement during the course of work, and to all of the technical and non-technical staffs for all the instances in which their assistance helped me along the way.\\
\indent		Above all, it was my family and friends who gave me endless support and provided me with an opportunity to reach this far with my studies. Their constant encouragement has always helped me to walk over all the hurdles. It’s just not possible to express my gratitude and indebtedness towards them in words. 

 



Last but not least, I thank almighty \textbf{\textit{\color{blue}Lord Vishwanath}} for providing me strength and courage in completing the work. 
\\
\\
\\
\\
\begin{flushright}
\begin{minipage}[t]{0.40\linewidth}
\begin{tabular}{ll}
\textbf{\textit{Pravin Bharat Solanki}}\\
\end{tabular}
\end{minipage}
\end{flushright}
